Add Data

### 2025-07-09 data.qmd

``````{cat}
#| engine.opts = list(file = "_data_dictionary.qmd"),
#| class.source = "md",
#| filename = "data_dictionary.qmd"

@@

``````{cat}
#| engine.opts = list(file = "_data_dictionary.qmd", append = TRUE),
#| class.source = "md",
#| filename = "data_dictionary.qmd"

>>>>

``````{cat}
#| engine.opts: { file: "_data_dictionary.qmd" }
#| class.source: "md"
#| filename: "data_dictionary.qmd"

@@

``````{cat}
#| engine.opts: { file: "_data_dictionary.qmd", append: TRUE }
#| class.source: "md"
#| filename: "data_dictionary.qmd"
